---
title: ""
author: ""
navbar: false

format: 
  html:
    theme: journal
    css: custom.css
editor: visual

knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false

googlesheets4::gs4_auth(path = "service-account.json")
googlesheets4::gs4_user()

cv_url <- "https://docs.google.com/spreadsheets/d/1nCw7ECSatsVa0cj-8g41b5qf3WX23PcSe3eWOXgkAuI/edit?usp=sharing"
cv <- googlesheets4::read_sheet(cv_url,
                                sheet = "entries",
                                skip = 1)
```

<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}

col_br_location <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<br><i class="fa-solid fa-location-dot"></i> ', col),
      ""
    )
}

create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, (lubridate::ymd(Sys.Date()))),
                  location = dplyr::if_else(location == "Online", NA_character_, location)) |>
    dplyr::filter(in_resume %in% c("TRUE"), section == section_name) |>
    dplyr::select(section:description_3) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == (lubridate::ymd(Sys.Date())) ~ glue::glue("Current <br> | <br> {format(start, '%b %Y')}"),
          end != start ~ glue::glue("{format(end, '%b %Y')} <br> | <br> {format(start, '%b %Y')}"),
          end == start ~ glue::glue("{format(end, '%b %Y')}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> *{col_br(institution)}* {col_br_location(location)}
          - {col_br(description_1)}
          - {col_br(description_2)} 
          - {col_br(description_3)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, location, description_1, description_2, description_3)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100),
                    table.border.top.style = "hidden",
                    table.border.bottom.style = "hidden") |> 
    gt::cols_align(align = "left", columns = main_text)
}

create_education_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, (lubridate::ymd(Sys.Date()))),
                  location = dplyr::if_else(location == "Online", NA_character_, location)) |>
    dplyr::filter(in_resume %in% c("TRUE"), section == section_name) |>
    dplyr::select(section:description_3) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == (lubridate::ymd(Sys.Date())) ~ glue::glue("Current <br> | <br> {format(start, '%b %Y')}"),
          end != start ~ glue::glue("{format(end, '%b %Y')} <br> | <br> {format(start, '%b %Y')}"),
          end == start ~ glue::glue("{format(end, '%b %Y')}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> *{col_br(institution)}* {col_br_location(location)} <br> {col_br(description_1)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, location, description_1, description_2, description_3)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |>
    gt::tab_options(column_labels.hidden = TRUE, 
                    table.width = gt::pct(100), 
                    table.border.top.style = "hidden",
                    table.border.bottom.style = "hidden"
                    ) |> 
    gt::cols_align(align = "left", columns = main_text)
}

create_projects_section <- function(cv_data, section_name){
    cv_data |>
        dplyr::mutate(in_resume = as.character(in_resume),
                      end = tidyr::replace_na(end, (lubridate::ymd(Sys.Date()))),
                      location = dplyr::if_else(location == "Online", NA_character_, location)) |>
        dplyr::filter(in_resume %in% c("TRUE"), section == section_name) |>
        dplyr::select(section:description_3) |>
        dplyr::arrange(desc(end), desc(start)) |>
        dplyr::mutate(
            date =
                dplyr::case_when(
                    end == (lubridate::ymd(Sys.Date())) ~ glue::glue("Current <br> | <br> {format(start, '%b %Y')}"),
                    end != start ~ glue::glue("{format(end, '%b %Y')} <br> | <br> {format(start, '%b %Y')}"),
                    end == start ~ glue::glue("{format(end, '%b %Y')}"),
                    TRUE ~ ""
                ) ,
            .before = everything()
        ) |>
        dplyr::mutate(
            main_header = dplyr::if_else(({col_br(institution)} == ""),
                                         glue::glue("**{title}**"),
                                         glue::glue("**{title}** <br> *{col_br(institution)}*")),
          .after = date) |>
        dplyr::mutate(
            main_description = dplyr::if_else(({col_br(description_1)} != "" & {col_br(description_2)} != "" & {col_br(description_3)} != ""), 
                                              glue::glue("<br> 
          - {col_br(description_1)}
          - {col_br(description_2)} 
          - {col_br(description_3)}"),
          dplyr::if_else(({col_br(description_1)} != "" & {col_br(description_2)} != ""), 
                         glue::glue("<br> 
          - {col_br(description_1)}
          - {col_br(description_2)}"),
          glue::glue("<br> 
          - {col_br(description_1)}"))),
          .after = date) |>
        dplyr::mutate(
            main_text = glue::glue("{main_header} {main_description}"),
            .after = date) |> 
        dplyr::select(-c(start, end, date, section, title, institution, location, description_1, description_2, description_3, main_header, main_description)) |>
        gt::gt() |>
        #gt::fmt_markdown(columns = c(date, main_text)) |> 
        gt::fmt_markdown(columns = c(main_text)) |> 
        gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100),
                        table.border.top.style = "hidden",
                        table.border.bottom.style = "hidden") |> 
        gt::cols_align(align = "left", columns = main_text)
}
```

<!-- Sidebar -->

::::: {#name .grid}
::: g-col-4
<center><a href='https://mohitshrestha.com.np' target='_blank'> ![](https://avatars.githubusercontent.com/u/47285145?v=4){width="80%" style="border-radius: 50%;"}</center>

</a>

### <i class="fa-solid fa-address-card"></i> Contact

<center><span style="font-size: 1.5em;"> <a href='https://mohitshrestha.com.np' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/MohitShrestha' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:mohitshrestha@gmail.com'><i class="fa fa-envelope"></i></a> <a href='tel:+14438234701'><i class="fa-solid fa-phone"></i></a> <a href='https://twitter.com/MohitShrestha' target='_blank'><i class="fa-brands fa-twitter"></i></a> <a href='https://linkedin.com/in/MohitShrestha' target='_blank'><i class="fab fa-linkedin"></i></a></center>

</span>

I am motivated to support organizations striving to be more data-driven in their missions and solve problems by converting insights from data into actionable solutions.

### <i class="fa-solid fa-laptop-code"></i> Programming skills

<i class="fab fa-r-project"></i> `R` / <i class="fa-brands fa-python"></i> `Python` <br> <i class="fa fa-area-chart" aria-hidden="true"></i> `tidyverse` <br> <i class="fab fa-markdown"></i> `RMarkdown / Quarto` <br> <i class="fas fa-code-branch"></i> `Git` / <i class="fab fa-github"></i> `GitHub` <br> <i class="fab fa-markdown"></i> `Markdown` <br> <i class="fab fa-html5"></i> `HTML` / <i class="fab fa-css3-alt"></i> `CSS` <br>

### <i class="fa-solid fa-person-chalkboard"></i> Teaching

**Graduate Peer Tutor**\
[*Wake Forest University School of Business*](https://business.wfu.edu/msbaprograms/)

Conducted one-on-one remote tutoring sessions for new cohort of MSBA students on the fundamentals of coding in SAS and R for Analytics Software Technology course

### <i class="fa-brands fa-dev"></i> Software

<i class="fas fa-box-open"></i> [Package {automaton}](https://mohitshrestha.github.io/automaton/) - Author.

### <i class="fa-solid fa-award"></i> Honors and Awards

<i class="far fa-star"></i> Patrick Henry Merit Scholarship <i class="far fa-star"></i> Phi Beta Kappa <i class="far fa-star"></i> Wall Street Journal Student Achievement Award <i class="far fa-star"></i> Pi Mu Epsilon <i class="far fa-star"></i> Omicron Delta Kappa <i class="far fa-star"></i> Chi Beta Phi <i class="far fa-star"></i> Omicron Delta Epsilon

### <i class="fa-solid fa-language"></i> Languages

**English:** Fluent <br> **Nepali:** Native <br> **Hindi:** Intermediate
:::

::: g-col-8
<!-- Main content -->

# Mohit Shrestha

I am well versed in R, Python, SAS, SQL, Tableau, and Power BI and specializes in data modeling and wrangling, building ML/AI models, analyzing and interpreting model results, and presenting impactful data insights to drive successful business solutions.

## <i class="fa-solid fa-suitcase"></i> Work Experiences

```{r}
create_section(cv, "industry_positions")
```

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_education_section(cv, "education")
```
:::
:::::

## <i class="fa-solid fa-chalkboard-user"></i> Selected Academic Research and Data Analytics projects

```{r}
create_projects_section(cv, "relevant_academic_research_and_data_analytics_projects")
```

<!-- footer -->

<p class="footer">

Resume made with 💜 and [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available on <i class="fa-brands fa-github"></i> [GitHub](https://github.com/mohitshrestha/resume/blob/master/docs/index.qmd). <br>License: [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/).

</p>

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
