---
title: ""
format: 
  html:
    theme: journal
    css: style.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- "https://docs.google.com/spreadsheets/d/1nCw7ECSatsVa0cj-8g41b5qf3WX23PcSe3eWOXgkAuI/edit?usp=sharing"
cv <- googlesheets4::read_sheet(cv_url,
                                sheet = "entries",
                                skip = 1)
```

<!-- Functions -->

{{< include create_sections_functions.qmd >}}

```{r, include=FALSE}
#source("create_sections_functions.r", local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
```

<!-- Sidebar -->

::: {#name .grid}
::: g-col-4
<center><a href='https://mohitshrestha.com.np' target='_blank'> ![](https://avatars.githubusercontent.com/u/47285145?v=4){width="80%" style="border-radius: 50%;"}</center>

</a>

### <i class="fa-solid fa-address-card"></i> Contact

<center><span style="font-size: 1.5em;"> <a href='https://mohitshrestha.com.np' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/MohitShrestha' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:mohitshrestha@gmail.com'><i class="fa fa-envelope"></i></a> <a href='tel:+14438234701'><i class="fa-solid fa-phone"></i></a> <a href='https://twitter.com/MohitShrestha' target='_blank'><i class="fa-brands fa-twitter"></i></a> <a href='https://linkedin.com/in/MohitShrestha' target='_blank'><i class="fab fa-linkedin"></i></a></center>

</span>

I am motivated to support organizations striving to be more data-driven in their missions and solve problems by converting insights from data into actionable solutions.

### <i class="fa-solid fa-laptop-code"></i> Programming skills

<i class="fab fa-r-project"></i> `R` / <i class="fa-brands fa-python"></i> `Python` <br> <i class="fa fa-area-chart" aria-hidden="true"></i> `tidyverse` <br> <i class="fab fa-markdown"></i> `RMarkdown / Quarto` <br> <i class="fas fa-code-branch"></i> `Git` / <i class="fab fa-github"></i> `GitHub` <br> <i class="fab fa-markdown"></i> `Markdown` <br> <i class="fab fa-html5"></i> `HTML` / <i class="fab fa-css3-alt"></i> `CSS` <br>

### <i class="fa-solid fa-person-chalkboard"></i> Teaching

**Graduate Peer Tutor**\
[*Wake Forest University School of Business*](https://business.wfu.edu/msbaprograms/)

Conducted one-on-one remote tutoring sessions for new cohort of MSBA students on the fundamentals of coding in SAS and R for Analytics Software Technology course

### <i class="fa-brands fa-dev"></i> Software

<i class="fas fa-box-open"></i> [Package {automaton}](https://mohitshrestha.github.io/automaton/) - Author.

### <i class="fa-solid fa-award"></i> Honors and Awards

<i class="far fa-star"></i> Patrick Henry Merit Scholarship <i class="far fa-star"></i> Phi Beta Kappa <i class="far fa-star"></i> Wall Street Journal Student Achievement Award <i class="far fa-star"></i> Pi Mu Epsilon <i class="far fa-star"></i> Omicron Delta Kappa <i class="far fa-star"></i> Chi Beta Phi <i class="far fa-star"></i> Omicron Delta Epsilon

### <i class="fa-solid fa-language"></i> Languages

**English:** Fluent <br> **Nepali:** Native <br> **Hindi:** Intermediate
:::

::: g-col-8
<!-- Main content -->

<h1><p class="name">Mohit Shrestha</p></h1>

I am well versed in R, Python, SAS, SQL, Tableau, and Power BI and specializes in data modeling and wrangling, building ML/AI models, analyzing and interpreting model results, and presenting impactful data insights to drive successful business solutions.

## <i class="fa-solid fa-suitcase"></i> Work Experiences

```{r}
create_section(cv, "industry_positions")
```

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_education_section(cv, "education")
```
:::
:::

## <i class="fa-solid fa-chalkboard-user"></i> Selected Academic Research and Data Analytics projects

```{r}
create_projects_section(cv, "relevant_academic_research_and_data_analytics_projects")
```

<!-- footer -->

<p class="footer">

Resume made with 💜 and [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available on <i class="fa-brands fa-github"></i> [GitHub](https://github.com/mohitshrestha/resume/blob/master/docs/index.qmd). <br>License: [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/).

</p>

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
